\chapter{Discussion}
\label{chap:discussion}

\cref{tab:discussion} was mainly compiled during the compilation of requirements, during implementation and during testing.

The table cannot be exhaustive!

The results only refer to the available images. As the images are less representative of the mainstream and more focused on problems, the result is probably not representative.

\begin{table}[htbp]
  \centering
  \caption[Comparison]{Comparison of different Products}
  \label{tab:discussion}
  \csvautobooktabular{csvtables/discussion.csv}
\end{table}

The following list is a supplement to the ratings in the table:

\begin{enumerate}
  \item APFS was not supported. Problems with ext4.
  \item There was no support for GNU/Linux. Problems with Bootcamp (macOS).
  \item The configuration of the VM has to be modified in Oracle VM VirtualBox GUI after creation.
  \item The configuration of the VM has to be modified in Oracle VM VirtualBox per command line after creation.
  \item GetData refers to PCUnlocker\footnote{https://www.top-password.com/reset-windows-password.html}, which must be purchased separately.
  \item Problems with Microsoft Windows 8, Bootcamp (macOS) and Dualboot (with Ubuntu).
  \item Problems with some macOS images.
  \item Problems with all GNU/Linux images.
  \item Only Microsoft Windows is supported.
  \item Only support for IDE, SCSI (default) and SATA.
  \item Problems with Bootcamp.
  \item APFS and ext4 was not supported.
  \item If Microsoft Windows drivers are available.
  \item The configuration of the VM has to be modified in HyperV after creation.
  \item Problems with some Images.
  \item Problems with some GNU/Linux images. Very slow on success.
\end{enumerate}

Even if the result suggests that the proprietary solutions performed poorly, it must be said at this point that they work good to very well for the mainstream.

The biggest advantage of propietary solutions over Hellonium are definitely the more intuitive user interfaces and the automatisms hidden behind them.

However, if the user has basic knowledge in the field of digital forensics, a big advantage of Hellonium is the greater flexibility and the support of the problem cases mentioned in this thesis.



Die Research question(s) erscheinen mir nicht mehr passend.

Vor einer Bewertung und einem Ergenbis sollten diese nochmal angepasst werden!
